L'extension \pkg{nicematrix} \thanks{Ce document correspond à la version~\myfileversion\space de \pkg{nicematrix}, en date du~\myfiledate.}

### 2020-08-14 MSU-thesis_estee_MaxFormat.tex
Almost finished. Acknowlegements added

\begin{dedication}
\centering
{\it
}
\end{dedication}

%% If you wish to have an acknowledgment, remove the "%" in front of  \begin{acknowledgment}
%% and remove the "%" in front of  \end{acknowledgment}  
\begin{acknowledgment}

>>>>

\begin{dedication}
\centering
{\it
To my wife for her unchanging support and patience\\ through this journey,
and to my flowering bud, Hanna. 
}
\end{dedication}

%% If you wish to have an acknowledgment, remove the "%" in front of  \begin{acknowledgment}
%% and remove the "%" in front of  \end{acknowledgment}  
\begin{acknowledgment}
This thesis encompassed many stages all the way from detector development and design, to setting up the experiments and the analysis of the data. This was a challenging thesis and its success can only be attributed to the collective effort of a relatively small group of very talented individuals. Without these people, this thesis would have not been successful, and the data would not have been of such high quality.

First, I would like to thank my advisor Professor Bill Lynch. It is through his extensive knowledge and experience that has guided me through this project and for giving me the opportunities to present my research at a wide range of conferences. I would like to thank him also for his though provoking dialogue, and for his dedication to making this project a success. I would like to also thank Professor Betty Tsang for her leadership, advice, and for keeping this project always on track to meet major milestones. I'm very thankful for the many thoughtful conversations and opportunities she has given me to really travel the world and network with many other people.

To my guidance committee, Profs. Pawe\l~ Danielewicz, Vladimir Zelevinsky, and Wade Fisher; I chose you all to be a part of my committee because of the impact you had made in my courses. Thank you for your time and effort you put into your lectures, and the effort put into advising and reviewing this thesis. I will cherish the memories.

I would like to also thank my greater collaboration, starting with the Japanese. Thank you Tadaaki Isobe and Mizuki Kurata-Nishimura, Professor Tetsuya Murakami, and Masanori Kaneko for leading the effort in Japan and seeing this experiment through. Isobe-san, I wanted to thank you especially for the hard work of setting up the DAQ and electronics of the TPC which really preformed flawlessly, considering how many subsystems were merged and the newness of the GET electronics. Mizuki-san, I always enjoyed working with you. You are a hard worker and without you the experimental setup, testing, and analysis could not have finished. Murakami-san, thank you for your support, advice, and wealth of knowledge. I considered you my advisor when I was away from home. Kaneko-san, thank you for working so diligently on the Kyoto array and the analysis. To Hidetada Baba, thank you for working on the electronics of our experiment, DAQ, and for introducing me to the wonders of Japanese Baseball. To all my friends at the University of Tokyo CNS for your friendship, softball, and hospitality. I also wanted to thank our Polish colleagues Jerzy \L ukasik, Piotr Paw\l owski, Krzysztof Pelczar, and Pawe\l \L asko for their hard work in developing the KATANA array and for setting up the trigger in the experiment.

I wanted to thank Jon Barney, my good friend; without you this project really would not be possible. I could always trust the work you did since you always dedicated yourself to this project. Thank you for getting me through the humps in graduate school and for always lending an ear. Thank you to Genie Jhang and JungWoo Lee, you wrote beautiful software for this project, and for the hard work done on the analysis, you both are really in a league of your own. It was no small task to write the majority of the code by yourselves. I've had the pleasure of working with Tommy Tsang who contributed a lot to the analysis of this project and worked double of the rest of us. Thank you also to Rensheng Wang. I've enjoyed our friendship and you are truly a great researcher and I could always count on you to help me think through a problem I could not solve.

I wanted to thank all of my postdocs whom I have not yet mentioned. To Bec Shane and Alan McIntosh, thank you for being the foundation of this project and for the long hours you poured into this. To Giordano Cerizza for the work that you did on the software, advice, and for our friendship. To Clemantine Santamaria, thank you for your friendship, and for your hard work setting up the experiment and for ensuring that our trigger ran well.

I am forever grateful to my mother and father for their continued support through my education. I am very blessed to have them as my parents. I wanted to thank my Aunts, Uncles, and Grandparents who have helped me financially and supported me throughout my schooling. To my Uncle Brian York, for his advice through the years and stimulating discussions.

Thank you to all the HiRA students through the years. I cherished my time with Juan Manfredi a true friend and great researcher. Thank you to the NSCL staff and RIKEN staff for making the construction and operation of this detector a success. Especially the BigRIPS team, RIBF cyclotron operators, and from the NSCL, John Puro, Jay Pline, Brian Drewyor, Ben Shuart, and John Yurkon for all of their advice, consulting, and ordering of parts.

I would also like to thank the funding sources which have made this all possible: the U.S. DOE under Grant Nos.DE-SC0014530, DE-NA0002923, US NSF GrantNo.PHY-1565546, and the Japanese MEXT KAKENHI grant No.24105004. The NSF EAPSI fellowship supporting my research at RIKEN for the summer of 2015(NSF award 1515450).

### 2020-08-14 chapters_altFormat/ch_data_analysis.tex
Almost finished. Acknowlegements added

\begin{figure}[!htb]%
    \centering
    \subfloat[$\mathrm{1^{st}}$ step of the PSA]{{\includegraphics[width=.4\textwidth,valign=t]{psa0.png} \label{fig:psa0}}}%
    \qquad
    \subfloat[$\mathrm{2^{nd}}$ iteration]{{\includegraphics[width=.24\textwidth,valign=c]{psa1.png} \label{fig:psa1}}}%
    \subfloat[$\mathrm{3^{nd}}$ iteration]{{\includegraphics[width=.24\textwidth,valign=c]{psa2.png} \label{fig:psa2}}}%
    \subfloat[$\mathrm{4^{nd}}$ iteration]{{\includegraphics[width=.24\textwidth,valign=c]{psa3.png} \label{fig:psa3}}}%
    \subfloat[Final output of the PSA]{{\includegraphics[width=.24\textwidth,valign=c]{psa4.png} \label{fig:psa}}}%

@@

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rrrrrrr@{}}\toprule
& \multicolumn{3}{c}{$100 MeV Target$}\\
\cmidrule{2-4}
Particle &\phantom{abc} & Measured & Corrected & \% Difference Raw & \% Difference Corrected\\
\midrule
p   & 882.8 & 929.5 & 877.3   &  3.7  & -1.0  \\
d   & 817.1 & 831.15 & 797.94 &  1.7  & -2.3\\
\bottomrule
\end{tabular}
\caption{Summary of expected cocktail for the calibration run taken with the Aluminum target. }
\label{tb:cocktail100tar}
\end{table*}

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rrrrrrr@{}}\toprule
& \multicolumn{3}{c}{$100 MeV$}\\
\cmidrule{2-4}
Particle & Expected & Measured & Corrected & \% Difference Raw & \% Difference Corrected\\
\midrule
p   & 882.8 & 903.5 & 889.0 &  2.0   & -1.6  \\
d   & 817.1 & 898.5 & 874.5 &  2.1   & -2.7\\
\bottomrule
\end{tabular}
\caption{Summary of expected cocktail from the lower beam energy.}
\label{tb:cocktail100}
\end{table*}

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rrrrrrr@{}}\toprule
& \multicolumn{3}{c}{$300 MeV$}\\
\cmidrule{2-4}
Particle & Expected & Measured & Corrected & \% Difference Raw & \% Difference Corrected\\
\midrule
d   & 1621 & 1704 & 1612   &  5.1 & -0.6  \\
t   & 1612 & 1691 & 1596   &  4.9  & -1.0\\
${}^{4}$He   & 1613 & 1698 &  1595 & 5.3 & -1.1\\

@@

\begin{figure}[!htb]
\includegraphics[width=\linewidth]{gaincalib.png}
\caption{Repose of each channel in the electronics to various input voltages of an input signal supplied by a pulse generator.}
\label{fig:gaincalib}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\linewidth]{highlowcal.png}
\caption{Calibration of low and high gain sections of the anode wires.}
\label{fig:highlowcal}
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=\linewidth]{intrographic}
%\includegraphics[width=\linewidth]{intrographic_2}
\caption{The expected $dE/dx$ lines of different particles are given in red as calculated by Geant4. The approximate dynamic range of the TPC is shown by the vertical bar for the gain setting used in the experiment. Anything outside of this region would be saturated to some degree.}
\label{fig:intro}
\end{figure}

@@

\begin{figure}[ht!]s
\begin{overpic}[width=\linewidth]{fig5.pdf}
\put(61,55){\contour{white}{ PRF${}_{\mathrm{Gaus}}(\lambda)$ eq. \ref{eq:gaus}  }}
\put(61,49){\contour{white}{ PRF${}_{\mathrm{Gatti}}(\lambda)$ eq. \ref{eq:gatti} }}
\end{overpic}
\caption{Experimental pad response function of many events for a crossing angle of $85^{\circ} < \theta \leq 90^{\circ}$.  }
\label{fig:expprf}
\end{figure}

@@

\begin{figure}[ht!]
\vspace{5mm}
\includegraphics[width=\linewidth]{fig7}
\caption{Parameters $N_{0}$ and $\sigma$ as a function of the crossing angle $\theta$ with the $4^{th}$ order polynomial fits.}
\label{fig:normsigma}
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=\linewidth]{saturated_pads}
\caption{A typical case of a saturating event. The red pulses represent the time bucket signal for each collected charge. The pads directly underneath the avalanche point, $q_{2'}$ and $q_{3'}$, are saturated while pads farther away, $q_1$ and $q_4$ are not saturated.}
\label{fig:satpad}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\linewidth]{spacechg_cartoon.png}
\caption{Cartoon diagram of the location of space charge for the ${}^{132}$Sn beam.}
\label{fig:spacechg_cartoon}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\linewidth]{beampath.png}
\caption{Beam path of the experiments}
\label{fig:beampaths}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\linewidth]{SC_Relation.pdf}
\caption{Relationship between the observable  $\Delta\mathrm{V}_\mathrm{LR}$ and the estimated charge density, and the beam intensity for each run. The blue and green line represents two separate runs at different beam intensities. The condition for  $\Delta\mathrm{V}_\mathrm{LR} = 0$ is solved for for each run. These values are then plotted against the beam intensity where finally a linear fit provides the interpolation for all beam intensities in between.}
\label{fig:spacechg_relation}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\linewidth]{spaceChgDensity.png}
\caption{Distribution of estimated space charge densities for each beam type.}
\label{fig:scDensity}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\linewidth]{VLRresidual.png}
\caption{Residuals in the fitted line of $\Delta V_{LR}$ observable for all systems.}
\label{fig:vlrResidual}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, before the space charge correciton.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_small_angle.pdf} \label{fig:psa0}}}%
    \qquad
    \subfloat[Comparison of the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} > \ang{40}$, before the space charge correction.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_large_angle.pdf} \label{fig:mom_L_before}}}\\
    \subfloat[Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, after the space charge correction.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_aftercor_small_angle.pdf} \label{fig:mom_S_after}}}%
    \qquad
    \subfloat[Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, after the space charge correction.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_aftercor_large_angle.pdf}  \label{fig:mom_L_after}}}%

>>>>

\begin{figure}[!htb]%
    \centering
    \subfloat[$\mathrm{1^{st}}$ step of the PSA]{{\includegraphics[width=.4\textwidth,valign=t]{psa0.png} \label{fig:psa0}}}%
    \qquad
    \subfloat[$\mathrm{2^{nd}}$ iteration]{{\includegraphics[width=.24\textwidth,valign=c]{psa1.png} \label{fig:psa1}}}%
    \subfloat[$\mathrm{3^{nd}}$ iteration]{{\includegraphics[width=.24\textwidth,valign=c]{psa2.png} \label{fig:psa2}}}%
    \subfloat[$\mathrm{4^{nd}}$ iteration]{{\includegraphics[width=.24\textwidth,valign=c]{psa3.png} \label{fig:psa3}}}%
    \subfloat[Final output of the PSA]{{\includegraphics[width=.24\textwidth,valign=c]{psa4.png} \label{fig:psa4}}}%

@@

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}ccccccc@{}}\toprule
& \multicolumn{3}{c}{$100 MeV Target$}\\
\cmidrule{2-4}
Particle &\phantom{abc} & Measured & Corrected & \% Difference Raw & \% Difference Corrected\\
\midrule
p   & 882.8 & 929.5 & 877.3   &  3.7  & -1.0  \\
d   & 817.1 & 831.15 & 797.94 &  1.7  & -2.3\\
\bottomrule
\end{tabular}
\caption{Summary of expected cocktail for the calibration run taken with the Aluminum target. }
\label{tb:cocktail100tar}
\end{table*}

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}ccccccc@{}}\toprule
& \multicolumn{3}{c}{$100 MeV$}\\
\cmidrule{2-4}
Particle & Expected & Measured & Corrected & \% Difference Raw & \% Difference Corrected\\
\midrule
p   & 882.8 & 903.5 & 889.0 &  2.0   & -1.6  \\
d   & 817.1 & 898.5 & 874.5 &  2.1   & -2.7\\
\bottomrule
\end{tabular}
\caption{Summary of expected cocktail from the lower beam energy.}
\label{tb:cocktail100}
\end{table*}

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}ccccccc@{}}\toprule
& \multicolumn{3}{c}{$300 MeV$}\\
\cmidrule{2-4}
Particle & Expected & Measured & Corrected & \% Difference Raw & \% Difference Corrected\\
\midrule
d   & 1621 & 1704 & 1612   &  5.1 & -0.6  \\
t   & 1612 & 1691 & 1596   &  4.9  & -1.0\\
${}^{4}$He   & 1613 & 1698 &  1595 & 5.3 & -1.1\\

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\linewidth]{gaincalib.png}
\caption{Repose of each channel in the electronics to various input voltages of an input signal supplied by a pulse generator.}
\label{fig:gaincalib}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\linewidth]{highlowcal.png}
\caption{Calibration of low and high gain sections of the anode wires.}
\label{fig:highlowcal}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=\linewidth]{intrographic}
%\includegraphics[width=\linewidth]{intrographic_2}
\caption{The expected $dE/dx$ lines of different particles are given in red as calculated by Geant4. The approximate dynamic range of the TPC is shown by the vertical bar for the gain setting used in the experiment. Anything outside of this region would be saturated to some degree.}
\label{fig:intro}
\end{figure}

@@

@@

\begin{figure}[ht!]
\centering
\vspace{5mm}
\includegraphics[width=\linewidth]{fig7}
\caption{Parameters $N_{0}$ and $\sigma$ as a function of the crossing angle $\theta$ with the $4^{th}$ order polynomial fits.}
\label{fig:normsigma}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=\linewidth]{saturated_pads}
\caption{A typical case of a saturating event. The red pulses represent the time bucket signal for each collected charge. The pads directly underneath the avalanche point, $q_{2'}$ and $q_{3'}$, are saturated while pads farther away, $q_1$ and $q_4$ are not saturated.}
\label{fig:satpad}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=.8\linewidth]{spacechg_cartoon.png}
\caption{Cartoon diagram of the location of space charge for the ${}^{132}$Sn beam.}
\label{fig:spacechg_cartoon}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=.8\linewidth]{beampath.png}
\caption{Beam path of the experiments}
\label{fig:beampaths}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\linewidth]{SC_Relation.pdf}
\caption{Relationship between the observable  $\Delta\mathrm{V}_\mathrm{LR}$ and the estimated charge density, and the beam intensity for each run. The blue and green line represents two separate runs at different beam intensities. The condition for  $\Delta\mathrm{V}_\mathrm{LR} = 0$ is solved for for each run. These values are then plotted against the beam intensity where finally a linear fit provides the interpolation for all beam intensities in between.}
\label{fig:spacechg_relation}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\linewidth]{spaceChgDensity.png}
\caption{Distribution of estimated space charge densities for each beam type.}
\label{fig:scDensity}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\linewidth]{VLRresidual.png}
\caption{Residuals in the fitted line of $\Delta V_{LR}$ observable for all systems.}
\label{fig:vlrResidual}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, before the space charge correciton.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_small_angle.pdf} \label{fig:mom_S_before}}}%
    \qquad
    \subfloat[Comparison of the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} > \ang{40}$, before the space charge correction.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_large_angle.pdf} \label{fig:mom_L_before}}}\\
    \subfloat[Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, after the space charge correction.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_aftercor_small_angle.pdf} \label{fig:mom_S_after}}}%
    \qquad
    \subfloat[Compare the momentum before and after including the BDC vertex for tracks with $\theta_{Lab} < \ang{40}$, after the space charge correction.]{{\includegraphics[width=.45\textwidth,valign=c]{BDC_P_aftercor_large_angle.pdf}  \label{fig:mom_L_after}}}%

### 2020-08-14 chapters_altFormat/ch_data_analysis_2.tex
Almost finished. Acknowlegements added

\begin{figure}[htb]
\centering
\includegraphics[scale=.5]{error_b_full.pdf}
\caption{Estimate of the impact parameter from the track multiplicity.}
\label{fig:impactPar}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[ $\tin{108}{112}$ system. ]{{\includegraphics[width=.46\textwidth,valign=c]{angularCut-pim-Sn108.png} \label{fig:pim108angle}}}%
    \qquad
    \subfloat[$\tin{132}{124}$ system. ]{{\includegraphics[width=.46\textwidth,valign=c]{angularCut-pim-Sn132.png} \label{fig:pim132angle}}}%

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[ $\tin{108}{112}$ system.]{{\includegraphics[width=.46\textwidth,valign=c]{angularCut-pip-Sn108.png} \label{fig:pip108angle}}}%
    \qquad
    \subfloat[$\tin{132}{124}$ system.]{{\includegraphics[width=.46\textwidth,valign=c]{angularCut-pip-Sn132.png} \label{fig:pip132angle}}}%
     \caption{Measured $\pi^+$ angular distribution for the two spherical angles $\theta$ and $\phi$.}
        \label{fig:pip}
\end{figure}

@@

\begin{equation}
A = \begin{pmatrix}
1 & 0 & 0 & 0\\
0 & 1 & 0 & 0\\
0 & 0 & \gamma & -\beta \gamma\\
0 & 0 & -\beta \gamma & \gamma
\end{pmatrix},
\end{equation}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[scale=.5]{error_b_full.pdf}
\caption{Estimate of the impact parameter from the track multiplicity from \cite{jon}.}
\label{fig:impactPar}
\end{figure}

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[ $\tin{108}{112}$ system. ]{{\includegraphics[width=.8\textwidth,valign=c]{angularCut-pim-Sn108.png} \label{fig:pim108angle}}}%
    \qquad
    \subfloat[$\tin{132}{124}$ system. ]{{\includegraphics[width=.8\textwidth,valign=c]{angularCut-pim-Sn132.png} \label{fig:pim132angle}}}%

@@

\begin{figure}[!htb]%
    \centering
    \subfloat[ $\tin{108}{112}$ system.]{{\includegraphics[width=.8\textwidth,valign=c]{angularCut-pip-Sn108.png} \label{fig:pip108angle}}}%
    \qquad
    \subfloat[$\tin{132}{124}$ system.]{{\includegraphics[width=.8\textwidth,valign=c]{angularCut-pip-Sn132.png} \label{fig:pip132angle}}}%
     \caption{Measured $\pi^+$ angular distribution for the two spherical angles $\theta$ and $\phi$.}
        \label{fig:pip}
\end{figure}

@@

\[ \left( \begin{array}{cccc}
1 & 0 & 0 & 0\\
0 & 1 & 0 & 0\\
0 & 0 & \gamma & -\beta \gamma \\
0 & 0 & -\beta \gamma & \gamma
\end{array} \right) \]

### 2020-08-14 chapters_altFormat/ch_experiment.tex
Almost finished. Acknowlegements added

 \begin{table*}[!htb]
 \centering
\ra{1.3}
\begin{tabular}{@{}rrrrrrr@{}}\toprule 
\multicolumn{2}{c}{GET electronics settings}\\
\midrule
 Plane & Material & Diameter \si{\micro\metre} & Pitch \si{\milli\metre} & Distance to pad-plane & Tension \si{\newton} & Voltage \si{\volt}\\ [0.5ex] 
 Anode  & Au-plated W   &  20  &  4  &  4   &  0.5  &  1460  \\
 Ground & BeCu          &  75  &  1  &  8   &  1.2  &  0     \\ 
 Gating & BeCu          &  75  &  1  &  14   &  1.2 &  -110$\pm$ 70\\ 
 \bottomrule
\end{tabular}
\caption{Wire plane properties.}
\label{tb:wireplane}
\end{table*}

In the open configuration, the gating grid is transparent to electrons coming from the field cage volume and also allows for ions to move from the avalanche region into the TPC volume. In the closed configuration it is opaque to electrons and ions, when set to the right voltages. Typically the gating grid is always in the closed configuration, only opening it momentarily when the data acquisition trigger criteria is met to take data. By keeping it always closed the electrons which come from the un-reacted beam are blocked,  which if allowed to go to the anode wires, would quickly build up enormous amounts of positive ions, flooding the field cage with space charge, distorting the electrons represnting the track paths. We open the gating grid for about \SI{11}{\micro\second} which is more than the time it takes for the electrons to drift 1 TPC volume. After this, we close the gating grid to prevent the back-flow of ions from the avalanche region from that event. Since ions move with a velocity much slower than that of electrons \cite{blumrol}, the ions only move several \si{\micro\metre} in the time the gate is open. This allows for electrons to pass through while preventing the back-flow of ions into the FC volume, reducing or even eliminating the space charge resulting from the avalanche region.

@@

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{gain.png}
\caption{Number of electrons produced in a single avalanche on an anode wire. Two different voltages were simulated using Garfield++ at 1470 $V$ and 1214 $V$. The expected Polya distribution fit is also given in yellow.}
\label{fig:anodegain}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{3boards_ps.jpg}
\caption{Figure of the pad plane boards being glued to the top plate. }
\label{fig:padplane}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\linewidth]{data.png}
\caption{Pad plane projection for a collision event in the TPC. Highlighted by red arrows are two regions of anode wires which had a reduced voltage of 1214 V. The voltage of the rest of the TPC anode wires are 1460 V. The reduction in voltage reduces the gain by a factor of about 10. }
\label{fig:data}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\linewidth]{cocktail.png}
\caption{Pad plane projection for a calibration event in the TPC.}
\label{fig:cocktail}
\end{figure}

>>>>

 \begin{table*}[!htb]
 \centering
\ra{1.1}
\begin{tabular}{@{}ccccccc@{}}\toprule 
\multicolumn{7}{c}{GET electronics settings}\\
\midrule
 Plane & Material & Diameter \si{\micro\metre} & Pitch \si{\milli\metre} & Distance to pad-plane \si{\milli\metre}& Tension \si{\newton} & Voltage \si{\volt}\\ [0.5ex] 
 Anode  & Au-plated W   &  20  &  4  &  4   &  0.5  &  1460  \\
 Ground & BeCu          &  75  &  1  &  8   &  1.2  &  0     \\ 
 Gating & BeCu          &  75  &  1  &  14   &  1.2 &  -110$\pm$ 70\\ 
 \bottomrule
\end{tabular}
\caption{Wire plane properties.}
\label{tb:wireplane}
\end{table*}

In the open configuration, the gating grid is transparent to electrons coming from the field cage volume and also allows for ions to move from the avalanche region into the TPC volume. In the closed configuration it is opaque to electrons and ions, when set to the right voltages. Typically the gating grid is always in the closed configuration, only opening it momentarily when the data acquisition trigger criteria is met to take data. By keeping it always closed the electrons which come from the un-reacted beam are blocked,  which if allowed to go to the anode wires, would quickly build up enormous amounts of positive ions, flooding the field cage with space charge, distorting the electrons represnting the track paths. We open the gating grid for about \SI{11}{\micro\second} which is more than the time it takes for the electrons to drift one TPC volume. After this, we close the gating grid to prevent the back-flow of ions from the avalanche region from that event. Since ions move with a velocity much slower than that of electrons \cite{blumrol}, the ions only move several \si{\micro\metre} in the time the gate is open. This allows for electrons to pass through while preventing the back-flow of ions into the FC volume, reducing or even eliminating the space charge resulting from the avalanche region.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=.8\textwidth]{gain.png}
\caption{Number of electrons produced in a single avalanche on an anode wire. Two different voltages were simulated using Garfield++ at 1470 $V$ and 1214 $V$. The expected Polya distribution fit is also given in yellow.}
\label{fig:anodegain}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=.8\textwidth]{3boards_ps.jpg}
\caption{Figure of the pad plane boards being glued to the top plate. }
\label{fig:padplane}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=.8\linewidth]{data.png}
\caption{Pad plane projection for a collision event in the TPC. Highlighted by red arrows are two regions of anode wires which had a reduced voltage of 1214 V. The voltage of the rest of the TPC anode wires are 1460 V. The reduction in voltage reduces the gain by a factor of about 10. }
\label{fig:data}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=.8\linewidth]{cocktail.png}
\caption{Pad plane projection for a calibration event in the TPC.}
\label{fig:cocktail}
\end{figure}
